WSClean: an implementation of a fast, generic wide-field imager for radio astronomy

### 2014-03-29 articles/2014/Article-WSClean/wsclean.tex
Renaming sdf to editmodel

In practice, the final scaling will be different from $\left(w_{\max} - w_{\min}\right)/\sqrt{1-l^2-m^2}$ suggested by Eq.~\eqref{eq:wstacking}, because the individual $w$-layers will not be completely filled with samples. Therefore, the number of added samples and their weight have to be taken into account. Therefore, each pixel is divided by the weighted number of samples. Additionally, it might be required to divide out the effect of a possible convolution kernel, the primary beam and correct for other direction-dependent effects. In XX, YY, LL or RR polarizations, a correlated baseline is the complex conjugate of the reversed baseline, and the relation $V(u,v,w)=\overline{V(-u,-v,-w)}$ holds. The right-hand side of Eq.\eqref{eq:wstacking} with only positive $w$-value samples then becomes the complex conjugate of the one with only negative $w$-value samples. In this case we can therefore calculate the image for $w<0$ from the image with $w>0$. That allows us to set $w_{\min}$ to the minimum absolute $w$-value, which requires half the number of layers. In any case, the input to the two-dimensional inverse FFT is not generally an Hermitian-symmetric function, and hence the inverse FFT is always performed as a complex-to-complex transform.

@@

\section*{Acknowledgments}
Offringa would like to thank O.M. Smirnov for testing \textsc{wsclean} on VLA data.
This scientific work makes use of the Murchison Radio-astronomy Observatory, operated by CSIRO. We acknowledge the Wajarri Yamatji people as the traditional owners of the Observatory site. Support for the MWA comes from the U.S. National Science Foundation (grants AST-0457585, PHY-0835713, CAREER-0847753, and AST-0908884), the Australian Research Council (LIEF grants LE0775621 and LE0882938), the U.S. Air Force Office of Scientific Research (grant FA9550-0510247), and the Centre for All-sky Astrophysics (an Australian Research Council Centre of Excellence funded by grant CE110001020). Support is also provided by the Smithsonian Astrophysical Observatory, the MIT School of Science, the Raman Research Institute, the Australian National University, and the Victoria University of Wellington (via grant MED-E1799 from the New Zealand Ministry of Economic Development and an IBM Shared University Research Grant). The Australian Federal government provides additional support via the Commonwealth Scientific and Industrial Research Organisation (CSIRO), National Collaborative Research Infrastructure Strategy, Education Investment Fund, and the Australia India Strategic Research Fund, and Astronomy Australia Limited, under contract to Curtin University. We acknowledge the iVEC Petabyte Data Store, the Initiative in Innovative Computing and the CUDA Center for Excellence sponsored by NVIDIA at Harvard University, and the International Centre for Radio Astronomy Research (ICRAR), a Joint Venture of Curtin University and The University of Western Australia, funded by the Western Australian State government.

>>>>

In practice, the final scaling will be different from $\left(w_{\max} - w_{\min}\right)/\sqrt{1-l^2-m^2}$ suggested by Eq.~\eqref{eq:wstacking}, because the individual $w$-layers will not be completely filled with samples. Therefore, each pixel is divided by the weighted number of samples. Additionally, it might be required to divide out the effect of a possible convolution kernel, the primary beam and correct for other direction-dependent effects. In equally-polarized baselines (e.g., XX, YY, LL or RR), a correlated baseline is the complex conjugate of the reversed baseline, and the relation $V(u,v,w)=\overline{V(-u,-v,-w)}$ holds. The right-hand side of Eq.\eqref{eq:wstacking} with only positive $w$-value samples then becomes the complex conjugate of the one with only negative $w$-value samples. In this case we can therefore calculate the image for $w<0$ from the image with $w>0$. That allows us to set $w_{\min}$ to the minimum absolute $w$-value, which requires half the number of layers. In any case, the input to the two-dimensional inverse FFT is not generally an Hermitian-symmetric function, and hence the inverse FFT is always performed as a complex-to-complex transform.

@@

\section*{Acknowledgments}
Offringa would like to thank O.~M.~Smirnov for testing \textsc{wsclean} on VLA data.
This scientific work makes use of the Murchison Radio-astronomy Observatory, operated by CSIRO. We acknowledge the Wajarri Yamatji people as the traditional owners of the Observatory site. Support for the MWA comes from the U.S. National Science Foundation (grants AST-0457585, PHY-0835713, CAREER-0847753, and AST-0908884), the Australian Research Council (LIEF grants LE0775621 and LE0882938), the U.S. Air Force Office of Scientific Research (grant FA9550-0510247), and the Centre for All-sky Astrophysics (an Australian Research Council Centre of Excellence funded by grant CE110001020). Support is also provided by the Smithsonian Astrophysical Observatory, the MIT School of Science, the Raman Research Institute, the Australian National University, and the Victoria University of Wellington (via grant MED-E1799 from the New Zealand Ministry of Economic Development and an IBM Shared University Research Grant). The Australian Federal government provides additional support via the Commonwealth Scientific and Industrial Research Organisation (CSIRO), National Collaborative Research Infrastructure Strategy, Education Investment Fund, and the Australia India Strategic Research Fund, and Astronomy Australia Limited, under contract to Curtin University. We acknowledge the iVEC Petabyte Data Store, the Initiative in Innovative Computing and the CUDA Center for Excellence sponsored by NVIDIA at Harvard University, and the International Centre for Radio Astronomy Research (ICRAR), a Joint Venture of Curtin University and The University of Western Australia, funded by the Western Australian State government.
